Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2025-02-10 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

# Demo Data --------------------------------------------
df_demo <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  filter(!LI06_05 %in% c(201, 223)) %>%  # Exclude participants without eye-tracking data
  transmute(
    Participant = LI06_05,
    `Teaching Experience` = LI04_01
  ) %>%
  arrange(Participant)

@@

# SRI Rating Data --------------------------------------------
# Data Import and Preprocessing ------------------------------------------
df_sri <- read_excel("data/Coding_SRI.xlsx") %>%
  filter(
    !ID %in% c(201, 223),  # Removing invalid IDs
    !disruption_appraisal %in% c(-100, -99, -88),  # Removing invalid disruption appraisals
    !confidence_appraisal %in% c(-100, -99, -88),  # Removing invalid confidence appraisals
    !prevalence_rating %in% c(-100, -99, -88)  # Removing invalid prevalence ratings
  ) %>%
  mutate(
    Group = ifelse(ID < 200, "Novice", "Expert"),  # Create a Group column based on ID
    Participant = ID,  # Keep ID as is for Participant column
    Disruption_Rating = as.numeric(disruption_appraisal),
    Confidence_Rating = as.numeric(confidence_appraisal),
    Prevalence_Rating = as.numeric(prevalence_rating)
  ) %>%
  select(-ID) %>% # Remove the original ID column after renaming
  arrange(Participant)

# Summarize the SRI Data for Disruptions and Overall Columns

# Step 1: Summarize appraisals for each disruption
df_sri_disrup_summary <- df_sri %>%
  filter(event %in% c(verbal_disruptions, lack_of_eagerness)) %>%
  group_by(Participant, event) %>%
  summarise(
    Disruption_Appraisal_Mean = mean(disruption_appraisal, na.rm = TRUE),
    Confidence_Appraisal_Mean = mean(confidence_appraisal, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(
    names_from = event,
    values_from = c(Disruption_Appraisal_Mean, Confidence_Appraisal_Mean),
    names_sep = "_"
  ) %>%
  mutate(across(everything(), ~ replace_na(., 0))) %>%   # Replace missing values with 0
  arrange(Participant)

# Step 2: Summarize overall appraisals by Participant
df_sri_clean <- df_sri %>%
  group_by(Participant) %>%
  summarise(
    Disruption_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
    Confidence_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  arrange(Participant)

# Combine both summaries (disruption-specific and overall)
df_sri_combined <- full_join(df_sri_clean, df_sri_disrup_summary, by = "Participant")

@@

# Ensure Participant is consistent across all dataframes
df_demo <- df_demo %>% mutate(Participant = as.numeric(Participant))
df_aoi_numb_dur <- df_aoi_numb_dur %>% mutate(Participant = as.numeric(Participant))
df_aoi_stud <- df_aoi_stud %>% mutate(Participant = as.numeric(Participant))
df_ttff_disrup_participant_summary <- df_ttff_disrup_participant_summary %>% mutate(Participant = as.numeric(Participant))
df_sri_combined <- df_sri_combined %>% mutate(Participant = as.numeric(Participant))
df_sjt <- df_sjt %>% mutate(Participant = as.numeric(Participant))
df_quest_summary <- df_quest_summary %>% mutate(Participant = as.numeric(Participant))

# Merge the dataframes
df_list <- list(
  df_demo,
  df_aoi_numb_dur,
  df_aoi_stud,
  df_ttff_disrup_participant_summary,
  df_sri_combined,
  df_sjt,
  df_quest_summary
)

@@

# 3. Correlation Analysis: Overall ---------------------------------------------
# 1. Select relevant variables for correlation analysis --------------------
df_correlation <- df_merge %>%
  select(
    Number_fixation_min_mtu, 
    Average_duration_mtu, 
    GRI_mtu, 
    Stud_number_fixation_min,
    log_Disrup_time_fixation_sec,
    Disruption_Rating, 
    Confidence_Rating, 
    SJT_All, 
    Self_Eval_Overall
  ) %>%
  drop_na()  # Remove rows with missing values for accurate correlation

# 2. Compute correlation coefficients and p-values ------------------------
cor_results <- rcorr(as.matrix(df_correlation))
cor_matrix <- cor_results$r  # Extract correlation coefficients
p_matrix <- cor_results$P    # Extract p-values

# 3. Reshape correlation coefficients and p-values into a tidy format -----
correlation_pvalues <- as.data.frame(as.table(cor_matrix)) %>%
  rename(Variable1 = Var1, Variable2 = Var2, Correlation = Freq) %>%
  left_join(
    as.data.frame(as.table(p_matrix)) %>%
      rename(Variable1 = Var1, Variable2 = Var2, P_value = Freq),
    by = c("Variable1", "Variable2")
  ) %>%
  filter(Variable1 != Variable2) %>%  # Remove redundant self-correlations
  mutate(
    Correlation = round(Correlation, 2),  # Round correlation coefficients
    P_value = round(P_value, 3),          # Round p-values
    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))  # APA formatting
  )

# 4. Create an APA-style correlation table --------------------------------------------
correlation_table <- correlation_pvalues %>%
  select(Variable1, Variable2, APA_Format) %>%
  pivot_wider(
    names_from = Variable2,
    values_from = APA_Format
  )

# Ensure Variable1 is a factor to maintain order
correlation_table$Variable1 <- factor(correlation_table$Variable1, levels = unique(correlation_table$Variable1))

# Convert to flextable for APA formatting
cor_flextable <- correlation_table %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  set_caption("Table 1: Correlation Table (APA Format)")

# Load required libraries
library(officer)
library(flextable)

# Ensure flextable is properly formatted
cor_flextable <- cor_flextable %>%
  fontsize(size = 11, part = "all") %>%  # Set font size
  bold(part = "header") %>%  # Make headers bold
  align(align = "center", part = "all") %>%  # Center align the text
  width(width = 1.5)  # Adjust column width

# Print table to check before saving (Debugging Step)
print(cor_flextable)

# 5. Save the table as a Word document --------------------------------------
doc <- read_docx() %>% 
  body_add_par("Table 1: Correlation Table (APA Format)", style = "heading 1") %>%
  body_add_par("", style = "Normal") %>%  # Add a blank space before the table
  body_add_flextable(cor_flextable) %>%
  body_add_par("", style = "Normal")  # Add blank space after the table

# Save the document
docx_path <- "Correlation_Table_APA.docx"
save_as_docx(doc, path = docx_path)

# Define the full file path explicitly
docx_path <- file.path(getwd(), "Correlation_Table_APA.docx")

# Save the document
save_as_docx(doc, path = docx_path)

# # 4. Correlation Analysis: Experts ---------------------------------------------
# 
# # Filter data for Experts (Participants with ID > 200)
# df_experts <- df_merge %>%
#   filter(Participant > 200) %>% 
#   select(-Participant)
# 
# # Compute correlation coefficients and p-values for Experts
# cor_results_experts <- rcorr(as.matrix(df_experts))
# cor_matrix_experts <- as.data.frame(cor_results_experts$r)  # Extract correlation coefficients
# p_matrix_experts <- as.data.frame(cor_results_experts$P)   # Extract p-values
# 
# # Reshape data into tidy format for Experts
# correlation_pvalues_experts <- cor_matrix_experts %>%
#   rownames_to_column(var = "Variable1") %>%
#   pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
#   left_join(
#     p_matrix_experts %>%
#       rownames_to_column(var = "Variable1") %>%
#       pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
#     by = c("Variable1", "Variable2")
#   ) %>%
#   mutate(
#     Correlation = round(Correlation, 2),
#     P_value = round(P_value, 2),
#     APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
#   )
# 
# # Create an APA-style table for Experts
# correlation_table_experts <- correlation_pvalues_experts %>%
#   select(Variable1, Variable2, APA_Format) %>%
#   pivot_wider(
#     names_from = Variable2,
#     values_from = APA_Format
#   )
# 
# # Display the Experts table
# kable(correlation_table_experts, format = "html", caption = "Correlation Table: Experts") %>%
#   kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))
# 
# 
# # 5. Correlation Analysis: Novices ---------------------------------------------
# 
# # Filter data for Novices (Participants with ID < 200)
# df_novices <- df_merge %>%
#   filter(Participant < 200) %>% 
#   select(-`Teaching Experience`,
#          -Participant)
# 
# # Compute correlation coefficients and p-values for Novices
# cor_results_novices <- rcorr(as.matrix(df_novices))
# cor_matrix_novices <- as.data.frame(cor_results_novices$r)  # Extract correlation coefficients
# p_matrix_novices <- as.data.frame(cor_results_novices$P)   # Extract p-values
# 
# # Reshape data into tidy format for Novices
# correlation_pvalues_novices <- cor_matrix_novices %>%
#   rownames_to_column(var = "Variable1") %>%
#   pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
#   left_join(
#     p_matrix_novices %>%
#       rownames_to_column(var = "Variable1") %>%
#       pivot_longer(-Variable1, names_to = "Variable2", values_to = "P_value"),
#     by = c("Variable1", "Variable2")
#   ) %>%
#   mutate(
#     Correlation = round(Correlation, 2),
#     P_value = round(P_value, 2),
#     APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
#   )
# 
# # Create an APA-style table for Novices
# correlation_table_novices <- correlation_pvalues_novices %>%
#   select(Variable1, Variable2, APA_Format) %>%
#   pivot_wider(
#     names_from = Variable2,
#     values_from = APA_Format
#   )
# 
# # Display the Novices table
# kable(correlation_table_novices, format = "html", caption = "Correlation Table: Novices") %>%
#   kable_styling(full_width = TRUE, bootstrap_options = c("striped", "hover", "condensed"))

>>>>

# Demo Data --------------------------------------------
df_demo <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  filter(!LI06_05 %in% c(201, 223)) %>%  # Exclude participants without eye-tracking data
  transmute(
    Participant = LI06_05,
    # `Teaching Experience` = LI04_01
  ) %>%
  arrange(Participant)

@@

# SRI Rating Data --------------------------------------------
# Data Import and Preprocessing ------------------------------------------
df_sri <- read_excel("data/Coding_SRI.xlsx") %>%
  filter(
    !ID %in% c(201, 223),  # Removing invalid IDs
    !disruption_appraisal %in% c(-100, -99, -88),  # Removing invalid disruption appraisals
    !confidence_appraisal %in% c(-100, -99, -88),  # Removing invalid confidence appraisals
    !prevalence_rating %in% c(-100, -99, -88)  # Removing invalid prevalence ratings
  ) %>%
  mutate(
    Participant = ID,  # Keep ID as is for Participant column
    Disruption_Rating = as.numeric(disruption_appraisal),
    Confidence_Rating = as.numeric(confidence_appraisal)
    )%>%
  select(Participant, 
         Disruption_Rating,
         Confidence_Rating) %>% # Remove the original ID column after renaming
  arrange(Participant) %>%
  group_by(Participant) %>%
  summarise(
    Disruption_Rating = round(mean(Disruption_Rating, na.rm = TRUE), 2),
    Confidence_Rating = round(mean(Confidence_Rating, na.rm = TRUE), 2)
  )

@@

# Ensure Participant is consistent across all dataframes
df_demo <- df_demo %>% mutate(Participant = as.numeric(Participant))
df_aoi_numb_dur <- df_aoi_numb_dur %>% mutate(Participant = as.numeric(Participant))
df_aoi_stud <- df_aoi_stud %>% mutate(Participant = as.numeric(Participant))
df_ttff_disrup_participant_summary <- df_ttff_disrup_participant_summary %>% mutate(Participant = as.numeric(Participant))
df_sri <- df_sri %>% mutate(Participant = as.numeric(Participant))
df_sjt <- df_sjt %>% mutate(Participant = as.numeric(Participant))
df_quest_summary <- df_quest_summary %>% mutate(Participant = as.numeric(Participant))

# Merge the dataframes
df_list <- list(
  df_demo,
  df_aoi_numb_dur,
  df_aoi_stud,
  df_ttff_disrup_participant_summary,
  df_sri,
  df_sjt,
  df_quest_summary
)

@@

# Separate Data by Experience Level
# Experienced teachers (ID > 200)
df_correlation_experienced <- df_merge %>%
  filter(Participant > 200) %>%
  select(
    Number_fixation_min_mtu, 
    Average_duration_mtu, 
    GRI, 
    Stud_number_fixation_min,
    log_Disrup_time_fixation_sec,
    Disruption_Rating, 
    Confidence_Rating, 
    SJT_All, 
    Self_Eval_Overall
  ) %>%
  drop_na()

# Inexperienced teachers (ID < 200)
df_correlation_inexperienced <- df_merge %>%
  filter(Participant < 200) %>%
  select(
    Average_duration_mtu,
    Number_fixation_min_mtu, 
    GRI, 
    Stud_number_fixation_min,
    log_Disrup_time_fixation_sec,
    Disruption_Rating, 
    Confidence_Rating, 
    Self_Eval_Overall,
    SJT_All
  ) %>%
  drop_na()

# Compute Correlations for Experienced Teachers
cor_results_experienced <- rcorr(as.matrix(df_correlation_experienced))
cor_matrix_experienced <- cor_results_experienced$r
p_matrix_experienced <- cor_results_experienced$P

# Compute Correlations for Inexperienced Teachers
cor_results_inexperienced <- rcorr(as.matrix(df_correlation_inexperienced))
cor_matrix_inexperienced <- cor_results_inexperienced$r
p_matrix_inexperienced <- cor_results_inexperienced$P

# Reshape correlation coefficients and p-values into a tidy format for experienced teachers
correlation_pvalues_experienced <- as.data.frame(as.table(cor_matrix_experienced)) %>%
  rename(Variable1 = Var1, Variable2 = Var2, Correlation = Freq) %>%
  left_join(
    as.data.frame(as.table(p_matrix_experienced)) %>%
      rename(Variable1 = Var1, Variable2 = Var2, P_value = Freq),
    by = c("Variable1", "Variable2")
  ) %>%
  filter(Variable1 != Variable2) %>%
  mutate(
    Correlation = round(Correlation, 2),
    P_value = round(P_value, 3),
    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
  )

# Reshape correlation coefficients and p-values into a tidy format for inexperienced teachers
correlation_pvalues_inexperienced <- as.data.frame(as.table(cor_matrix_inexperienced)) %>%
  rename(Variable1 = Var1, Variable2 = Var2, Correlation = Freq) %>%
  left_join(
    as.data.frame(as.table(p_matrix_inexperienced)) %>%
      rename(Variable1 = Var1, Variable2 = Var2, P_value = Freq),
    by = c("Variable1", "Variable2")
  ) %>%
  filter(Variable1 != Variable2) %>%
  mutate(
    Correlation = round(Correlation, 2),
    P_value = round(P_value, 3),
    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
  )

# Create correlation tables for both groups
correlation_table_experienced <- correlation_pvalues_experienced %>%
  select(Variable1, Variable2, APA_Format) %>%
  pivot_wider(names_from = Variable2, values_from = APA_Format)

correlation_table_inexperienced <- correlation_pvalues_inexperienced %>%
  select(Variable1, Variable2, APA_Format) %>%
  pivot_wider(names_from = Variable2, values_from = APA_Format)

# Ensure Variable1 is a factor to maintain order
correlation_table_experienced$Variable1 <- factor(correlation_table_experienced$Variable1, levels = unique(correlation_table_experienced$Variable1))
correlation_table_inexperienced$Variable1 <- factor(correlation_table_inexperienced$Variable1, levels = unique(correlation_table_inexperienced$Variable1))

# Convert to flextable for APA formatting
cor_flextable_experienced <- correlation_table_experienced %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  set_caption("Table 1: Correlation Table for Experienced Teachers")

cor_flextable_inexperienced <- correlation_table_inexperienced %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  set_caption("Table 2: Correlation Table for Inexperienced Teachers")
